Developing a preprint culture in biology

### 2012-09-28 ms.tex
start work on Ingelfinger, add refs
Ingelfinger

@@

Open preprints servers offer a great opportunity for open science, especially if
the community embrace the idea of discussing preprints. Initiatives like
Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a
new blog discussing arXiv papers in population genetics, will help make arXiv
attractive for scientists looking to promote their work. These initiatives are
important to fully exploit the potential of open preprints servers. Posting
preprints online increases the community of available informal peer reviewers,
and uses the internet for its original community-building purposes.  Preprint
servers also facilitate communication between disciplines, bridging cultural as
well as geographic divides. The advantages are clear and the costs are low.
Responding to the rumour that they refused manuscripts submitted to arXiv,
Nature responded that ``Nature never wishes to stand in the way of communication
between researchers. We seek rather to add value for authors and the community
at large in our peer review, selection and editing'' \cite{nat05}.

>>>>

Part of the hostility to preprints servers comes from a certain interpretation
of the Ingelfinger rule: scientists should not publish the same manuscript twice
\cite{alt96}. However, papers submitted to arXiv or other preprints servers are
only published in one peer-reviewed journal. A preprint is just a preprint, it
is a document that allows ideas to spread and be discussed, but it is not yet
formally validated by the peer-review system, which is why the majority of
publishers does not see arXiv and similar services as a violation of the
Ingelfinger rule. \emph{Nature} responded to the rumour that they refused
manuscripts submitted to arXiv by saying that ``\emph{Nature} never wishes to
stand in the way of communication between researchers. We seek rather to add
value for authors and the community at large in our peer review, selection and
editing'' \cite{nat05}.

% Discuss embargoes?
%A second potential problem is embargoes. Many publishers subject their article
%to embargoes \cite{rea12}.

@@

Open preprints servers offer a great opportunity for open science, especially if
the community embrace the idea of discussing preprints. Initiatives like
Haldane's Sieve (\href{http://haldanessieve.org/}{http://haldanessieve.org/}), a
new blog discussing arXiv papers in population genetics, will help make arXiv
attractive for scientists looking to promote their work. These initiatives are
important to fully exploit the potential of open preprints servers. Posting
preprints online increases the community of available informal peer reviewers,
and uses the internet for its original community-building purposes.  Preprint
servers also facilitate communication between disciplines, bridging cultural as
well as geographic divides. The advantages are clear and the costs are low.
